The relative roles of genetic, ecological and environmental factors in species radiations

### 2017-11-02 paper/draft.tex
fix
fix biblatex/biber
fix citation
csquotes
csquotes after inputenc
new angle for intro

\documentclass[a4paper]{scrartcl}
\usepackage[english]{babel}
\usepackage{natbib}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

@@

Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact that some lineages radiate explosively following
island colonisation, while others remain one single species (Price/Chase) (eg. \cite{price2004speciationPrice}).

@@

Using an individual-based mechanistic model we investigated how genetic, ecological and environmental factors colonisation and radiation histories on islands,
and what trait combinations constitute successful colonizer and radiator [this sounds like heating ;)] species, respectively.
\section{Material and Methods}

@@

\addbibresource{refs.bib}
\printbibliography

>>>>

\documentclass[a4paper]{scrartcl}
\usepackage[english]{babel}
\usepackage[
  backend=biber,
  style=authoryear
]{biblatex}
\addbibresource{refs.bib}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}

@@

Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact that some lineages radiate explosively following
island colonisation, while others remain one single species (Price/Chase) (eg. \cite{price2004speciation}).

@@

Using an individual-based mechanistic model we investigated how genetic, ecological and environmental factors colonisation and radiation histories on islands,
and what trait combinations constitute successful colonizer and radiating species, respectively.

[NEW ANGLE:]
island biota have always fascinated and inspired researchers (Darwin, Wallace, ...).
While often featuring unique species communities and harboring countless endemics,
islands are especially threatened by climate change, human impact and invasive species.

Because the study of islands biogeography takes into account evolutionary time frames (millions of years),
comprehensive and meaningful data is difficult to obtain.
In a recent review \cite{leidinger2017biodiversity}, we analyzed a powerful alternative to field experiments in island biogeography
--- mechanistic (/simulation) models.
Unfortunately, most island models failed to include more explicit genetic or micro evolution.
Instead some models featured a concept known as ``protracted speciaton'' \cite{rosindellXXX}, where speciation occurs with a delay from the actual
divergence event if the population remains isolated during that time.

\section{Material and Methods}

@@

\printbibliography
